Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-29 datapaper_hardware.tex
small typo fix in hardware section

The depth sensor is limited largely by the strength of the signal returned.  Low-reflectivity surfaces, such as the foam under the plant leaves, are accurate only at a close range (on the order of $20$ or $30~cm$).  On the other hand, specular and highly reflective objects, such metal and plastic surfaces in the growth chamber, can saturate the sensor pixels leading to unreliable depths for those pixels.  Fortunately the primary goal of the depth sensor is to obtain leaf pixel depths, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.  As a result the most useful and reliable depth pixels that those that fall on plant foliage, and we usually ignore non-foliage pixel depths.

>>>>

The depth sensor is limited largely by the strength of the signal returned.  Low-reflectivity surfaces, such as the foam under the plant leaves, are accurate only at close range (on the order of $20$ or $30~cm$).  On the other hand, specular and highly reflective objects, such metal and plastic surfaces in the growth chamber, can saturate the sensor pixels leading to unreliable depths for those pixels.  Fortunately the primary goal of the depth sensor is to obtain depths of leaf pixels, and plants provide good, roughly Lambertian, reflections of IR~\cite{Chelle2006219}.  As a result the most useful and reliable depth pixels are those that fall on plant foliage, and we usually ignore non-foliage pixel depths.
